--- 
title: "PADP 7120 R Chapters"
subtitle: "Learning Concepts and Skills Through R"
author: "Alex Combs"
date: "Last updated on `r format(Sys.time(), '%d %B %Y')`"
site: bookdown::bookdown_site
documentclass: book
biblio-style: apalike
link-citations: yes
colorlinks: yes
lot: false
lof: false
description: "Homework for PADP 7120"
url:  'https://alex-combs.github.io/data-apps-homework/'
github-repo: "alex-combs/data-apps-homework"
always_allow_html: yes
---

# Preface {-}

This is a collection assignments called R Chapters for students enrolled in my section of PADP 7120: Data Applications in Public Administration. Students who intend to use a personal computer to complete exercises in the R chapters need to download and install the following software:

- [R](https://cloud.r-project.org)
- [RStudio](https://rstudio.com/products/rstudio/download/)

```{r bookpacks, include=FALSE}
library(tidyverse)
library(knitr)
library(arsenal)
library(forecast)
library(fpp2)
library(lubridate)
library(readxl)
library(plm)
library(broom)
library(car)
library(gvlma)
library(gapminder)
library(Ecdat)
library(carData)
library(openintro)
library(fivethirtyeight)
library(moderndive)
library(DAAG)
library(Stat2Data)
library(data.table)
```

```{r set-options, include=FALSE, purl=FALSE}
# Set output options
if (is_html_output()) {
  options(width = 80)
}
if (is_latex_output()) {
  options(width = 75)
}
options(digits = 7, bookdown.clean_book = TRUE, knitr.kable.NA = "NA")
opts_chunk$set(
  tidy = FALSE,
  out.width = "\\textwidth",
  fig.align = "center",
  comment = NA
)

# To get kable tables to print nicely in .tex file
if (is_latex_output()) {
  options(kableExtra.auto_format = FALSE, knitr.table.format = "latex")
}
```
<br>

<p xmlns:dct="http://purl.org/dc/terms/" xmlns:cc="http://creativecommons.org/ns#" class="license-text"><span rel="dct:title">Data Applications in Public Administration</span> by <a rel="cc:attributionURL dct:creator" property="cc:attributionName" href="https://alex-combs.github.io/web-work/index.html">Alex Combs</a> is licensed under <a rel="license" href="https://creativecommons.org/licenses/by-nc-nd/4.0">CC BY-NC-ND 4.0<img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/cc.svg?ref=chooser-v1" /><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/by.svg?ref=chooser-v1" /><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/nc.svg?ref=chooser-v1" /><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/nd.svg?ref=chooser-v1" /></a></p>